%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10.9pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Nishant Raj} \\ \vspace{1pt}
    \small 9311238361 $|$ \href{mailto:nishant.read@gmail.com}{\underline{nishant.read@gmail.com}} $|$ 
    \href{https://linkedin.com/in/nishantunderstand}{\underline{linkedin.com/in/nishantunderstand}}
\end{center}

%-----------PROFILE SUMMARY-----------
\section*{Profile Summary}
\noindent
Java Backend Developer with \textbf{3.6+ years} of experience in building Spring Boot applications and REST APIs. Proficient in Spring MVC, JPA, Security, multithreading, exception handling, and unit testing with JUnit/Mockito.


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tata Consultancy Services (TCS)}{Jan 2023 -- Present}
      {Java Backend Engineer}{Noida, India}

      \resumeSubSubheading
        {Walgreens Boots Alliance}{}{}{}
        \resumeItemListStart
          \resumeItem{Reduced critical downtime incidents by \textbf{60\%} through proactive fault detection mechanisms on production servers.}
          \resumeItem{Integrated payment gateway flow using Worldpay, resulting in a \textbf{90\%} reduction in failed transactions and improved customer checkout experience.}
          \resumeItem{Spearheaded development and maintenance of a robust payment module using \textbf{Java, Hibernate, JPA, and Lombok}, streamlining transactions across services.}
          \resumeItem{Implemented comprehensive unit and integration test suites with \textbf{JUnit} and \textbf{Mockito}, increasing test coverage by \textbf{30\%} and reducing post-deployment bugs by \textbf{20\%}.}
        \resumeItemListEnd

      \resumeSubSubheading
        {Carasoft}{}{}{}
        \resumeItemListStart
          \resumeItem{Redesigned the user notifications module from the ground up, leading to a \textbf{40\%} increase in user engagement and system responsiveness.}
          \resumeItem{Engineered secure permission handling with RBAC and \textbf{JWT authentication}, cutting access-related bugs by \textbf{90\%} and hardening the system's security.}
          \resumeItem{Established structured error logging using \textbf{Apache Log4j}, improving root cause analysis speed by \textbf{45\%} across \textbf{20+} microservices.}
        \resumeItemListEnd

        \resumeSubheading
          {Tech Mahindra}{Aug 2021 -- Sep 2022}
          {Associate Software Engineer}{Noida, India}
        \resumeSubSubheading
          {Mountain Crew}{} 
        \resumeItemListStart
          \resumeItem{Owned module-wise documentation for the \textbf{Mountain Crew} project, detailing data flows, mappings, and exception handling to enhance developer onboarding and maintainability.}
          \resumeItem{Managed \textbf{JDBC} thread connection pooling for optimized and consistent database operations under concurrent load.}
          \resumeItem{Implemented multi-threaded data processors using Java concurrency APIs such as \textbf{Fork-Join}, \textbf{Synchronization}, and the \textbf{Executor Framework}.}
          \resumeItem{Diagnosed and resolved high-priority production incidents via \textbf{GCP Log Server}, reducing mean time to recovery (MTTR).}
        \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Java (Core Java, Java 8), SQL, Shell/BAT Scripts} \\
    \textbf{Frameworks \& Libraries}{: Spring Boot, Spring MVC, Spring Security, Hibernate, JUnit, Mockito, Log4j, RESTful APIs} \\
    \textbf{Microservices \& Architecture}{: Microservices, JWT, RBAC, Apache Kafka, Threading (Executor Service, Fork-Join), HikariCP} \\
    \textbf{Tools \& Platforms}{: Git, TortoiseGit, Maven, Jenkins, Docker, Postman, SOAP UI, CMD, PowerShell} \\
    \textbf{IDEs}{: IntelliJ IDEA, Eclipse, VS Code} \\
    \textbf{Databases}{: IBM DB2, MySQL, Oracle DB} \\
    \textbf{Cloud \& Monitoring}{: Google Cloud Platform (Certified), Microsoft Azure Fundamentals (AZ-900), Apache Log4j, GCP Log Server}
  }}
\end{itemize}




%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dr. Akhilesh Das Gupta Institute of Technology and Management}{New Delhi}
      {Bachelor of Technology in Computer Science; GPA: 7.63/10}{Aug. 2016 -- Nov. 2020}
    \resumeSubheading
      {Central Academy Senior Secondary School}{Rajasthan}
      {Intermediate; CGPA: 8.2}{Apr. 2014 -- May. 2015}
    \resumeSubheading
      {Sarvodaya Bal Vidyalaya}{New Delhi}
      {High School; CGPA: 8.4}{Apr. 2012 -- May. 2013}
  \resumeSubHeadingListEnd




%-------------------------------------------
\end{document}
